% LaTeX resume using res.cls
\documentclass[margin, line]{res}
\topmargin=-0.5in
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
\usepackage{enumitem}
\setlist{nosep}

\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Brendon Egolf}
% Draw a horizontal line the whole width of resume:
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{09770 Springvale Rd. $\bullet$ Boyne Falls, MI 49713}
 \moveleft.5\hoffset\centerline{Cell: (989)233-5663}
 \moveleft.5\hoffset\centerline{begolf123@gmail.com}


\begin{resume}
\noindent

  \section{EDUCATION} {\sl Petoskey High School}, Petoskey, MI \hfill \textbf{June 2017} \\
                \begin{itemize}
                    \item GPA: 3.5
                    \item ACT: 32
                    \item AP Computer Science, AP Calculus, Honors Physics, AP Physics II, AP
                    Economics
                    \item Dual Enrollment with North Central Michigan College: UNIX I,
                      and CNC Machining 100
                \end{itemize}

{\sl Rose Hulman Institute of Technology}, Terre Haute, IN \\
                \begin{itemize}
                  \item Participated in Fast Track Calculus, a five week intensive
                    course teaching Calculus I, II, and III.
                  \item GPA: 3.28
                \end{itemize}

\section{SKILLS}
  \begin{itemize}
    \item Proficient with Microsoft Word and PowerPoint
    \item Advanced knowledge of Excel (macros, VLOOKUP, INDIRECT, etc.)
    \item Strong customer service skills in a sales environment
    \item Experience with AS/400 mainframe software
    \item Detailed knowledge of GNU Linux and the bash shell
    \item Proficient with \LaTeX document formatting
    \item Proficient with MEAN Stack web development
    \item Intermediate Python
    \item Intermediate BASH Scripting
    \item Intermediate Perl 5 \& 6
  \end{itemize}

  \section{EXPERIENCE}
    {\sl Web Developer} \hfill RealtyPro Websites \hfill \textbf{June 2016
    - August 2016} \\
  \begin{itemize}
    \item Converted static web templates to integrate with the company's
      Content Management System
  \end{itemize}

    {\sl Web Developer} \hfill Bear River Electric \hfill \textbf{June 2017
    - September 2017} \\
  \begin{itemize}
    \item Created a website that allowed employees to submit Time \& Materials sheets,
      time cards, and company files.

    \item Setup a web server to host said website and file storage.
  \end{itemize}

    {\sl Customer Pickup Associate} \hfill Art Van Furniture \hfill \textbf{June 2018
    - December 2018} \\
  \begin{itemize}
    \item Assisted guests in loading furniture into their vehicle.
  \end{itemize}

    {\sl Customer Pickup Associate} \hfill Art Van Furniture \hfill \textbf{December
    2018 - Present} \\
  \begin{itemize}
    \item Tender invoices for customers.

    \item Manage delivery scheduling and inventory.

    \item Effectively resolve customer concerns via phone and in person.

    \item Created macros for mainframe software to improve productivity.

  \end{itemize}

\section{COMMUNITY \\ SERVICE}
    \begin{itemize}
      \item 3 time participant in the annual Clean the Bear project
      \item 2 time FIRST Tech Challenge Regional competition volunteer
      \item Programming mentor for Middle School Robotics team
      \item Instructed a six week class on introductory python at local library
    \end{itemize}

\section{ACTIVITIES}
\begin{itemize}
  \item FIRST Robotics (Freshman - Senior Year), Accounting Captain Junior Year, Programming Captain Senior Year
  \item Policy Debate (Freshman - Junior Year), GVSU JV Champion, DUDL JV Champion
  \item Tutor for Honors Physics class (Senior Year)
\end{itemize}
\end{resume}
\end{document}




